Information Retrieval - Submission Report \\Project N.14: Art For Sale

### 2023-12-11 docs/report/submission.tex
feat: submission report finished
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

    \subsection{Dowload}
    The complete code exceeded the size allowed by iCorsi. For this reason, the repository can be found at \url{https://github.com/JekxDevil/IR-ArtForSale}

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Evaluation}\label{sec:evaluation}
    Part of the \textbf{Query and Retrieval Process}, regarding \textbf{Evaluation}.\\
    \textbf{Effectiveness}: quality of results.
    Employing of \textbf{query expansion} was tested by always adding the \textit{art} keywork
    at the end of each search to get more results.
    This led to under-constrained query giving back not relevant results.
    The reason was due to the fact that for our specific set of concerns, hence documents, the word
    \textit{"art"} is an high frequency word, thus useless to achieve pertinency as explained by
    \textbf{Zipf's Law}.

    At start, every field was in a \textit{pandas.Series} and then given to the indexer but this lead to
    unsatisfying results: it seemed like only the first field (title) got indexed,
    giving an \textbf{over-constrained query} feeling where either no documents or no relevant ones were returned,
    Hence we decided to put every field into one big "blob" of text and then indexed that.\\
    \textbf{Efficiency}: response time and throughput.
    Since there is no pagination of results, all the list of relevant documents is sent and shown at once
    in the single page.
    This can lead to queries that give back hundred of documents and the response time to render them is high
    and has been partially leverage in the UX by adding a loader animation for retrieval,
    shown in Figure \ref{fig:loader}.

    \subsection{User Evaluation}
    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}.\\
    The conducted SUS modules are in \textit{docs/user-evaluation.pdf}.
    After the development, we have conduct an user evaluation on 5 different users using the SUS questionnaire.
    The SUS questionnaire is a 10-item questionnaire that measures the usability of a system.
    Each question is rated on a 5-point Likert scale, from strongly disagree to strongly agree.
    At the end of the questionnaire, we can compute the SUS score, which is a number between 0 and 100
    that indicates how usable the system is.
    We asked 5 users to use the system and fill the SUS questionnaire.
    While using the system we asked them to perform some tasks, such as searching for artworks,
    check the recommendations and use the filters.
    Sentiment analysis: all the users found the system intuitive and well-structured,
    without needing particular help to perform the various tasks.
    Once computed, we have obtained a 91.5\% SUS score.
    Given the results of the SUS questionnaire, we can say that the system is definitely usable
    and that the users are satisfied with it.

@@

>>>>

    \subsection{Dowload}
    The complete code exceeded the size allowed by iCorsi.
    For this reason, the repository can be found at
    \url{https://github.com/JekxDevil/IR-ArtForSale}.
    The release at submission is \textit{submission} with tag \textit{v1.0.0} and commit hash
    \textit{asdfasdfasdf}.

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Evaluation}\label{sec:evaluation}
    Part of the \textbf{Query and Retrieval Process}, regarding \textbf{Evaluation}.\\
    \newline
    \textbf{Effectiveness}: quality of results.\\
    An attempt to improve effectiveness was employing of \textbf{query expansion},
    tested by always adding the \textit{art} keywork at the end of each search to get more results.
    This led to under-constrained query giving back not relevant results.
    The reason was due to the fact that for our specific set of concerns, hence documents, the word
    \textit{"art"} is an high frequency word, thus useless to achieve pertinency as explained by
    \textbf{Zipf's Law}.\\
    A change to improve effectiveness was done when we noticed that at start,
    every field was in a \textit{pandas.Series} and then given to the indexer but this lead to
    unsatisfying results: it seemed like only the first field (title) got indexed,
    giving an \textbf{over-constrained query} feeling where
    either no documents or no relevant ones were returned,
    Hence we decided to put every field into one big "blob" of text and then indexed that.\\
    \newline
    \textbf{Efficiency}: response time and throughput.\\
    Since there is no pagination of results, all the list of relevant documents is sent
    and shown at once in the single page.
    This can lead to queries that give back hundred of documents
    and the response time to render them is high and has been partially leveraged
    in the UX by adding a loader animation for retrieval as shown in Figure \ref{fig:loader}.

@@

    \subsection{User Evaluation}
    Part of the \textbf{Relevance Feedback Process}, regarding \textbf{User Evaluation}.\\
    The conducted SUS modules are in \textit{docs/user-evaluation.pdf}.
    After the development, we conducted an user evaluation on 5 different users
    using the \textbf{SUS questionnaire}.
    The SUS questionnaire is a 10-item questionnaire that measures the usability of a system.
    Each question is rated on a 5-point Likert scale, from strongly disagree to strongly agree.
    At the end of the questionnaire, we can compute the SUS score, which is a number
    between 0 and 100 that indicates how usable the system is.
    We asked 5 users to use the system, fill the SUS questionnaire and signing it.
    While using the system we asked them to perform the following tasks:
    \begin{itemize}
        \setlength\itemsep{0.1em}
        \item familiaze for 10 seconds with the platform
        \item search for an artwork
        \item try out the filters
        \item check the suggested recommendations
    \end{itemize}
    The first 3 SUS forms were done a week before the submission, hence we had the time to
    implement the suggested enhancements during the last sprint iteration of development:
    \begin{itemize}
        \setlength\itemsep{0.1em}
        \item put the recommendation carousel on a side
        \item reset of filters after each search
        \item adjust card size
        \item add a spinner during loading of results since it is not intuitive it is loading them
        \item add enter event listener to search bar to directly query the system
    \end{itemize}

    \underline{Sentiment analysis}: all users found the system intuitive and well-structured,
    without needing particular help to perform the various tasks.
    Once computed, we have obtained a 91.5\% SUS score.
    Given the results of the SUS questionnaire, we can say that the system is definitely usable
    and that the users are satisfied with it.
